---
title: "Analysis — Bargaining Power and Aid for Trade"
output: html_notebook
---

Builds the bargaining-power construct (`alpha`) from the panel produced by
`code/01_build_dataset.R`, estimates the SUR model, runs the dyad cluster
bootstrap, and produces the paper's figures and robustness checks.

```{r message=FALSE, warning=FALSE}
source(here::here("code/00_packages.R"))
CRS_Data <- read_excel(here::here("data/processed/CRS_Data.xlsx"))
```

### Data preparation:

```{r}
colnames(CRS_Data)
```

```{r warning=FALSE}
# Coerce raw columns to numeric:

num_cols <- c("USD_Disbursement", "Other_AfT", "COL_FR","COL_UK","COL_US","COL_JP","distwces",
              "Foreign_pop", "VA", "Cost_Trade", "cc","pv","rq","rl","ge", "external_debt", "total_reserves", "gdp_growth")
CRS_Data <- CRS_Data %>%
  mutate(across(all_of(intersect(num_cols, names(CRS_Data))),
                ~ suppressWarnings(as.numeric(.))))
```

```{r warning=FALSE}
# DV + dyadic transformation:

CRS_Data <- CRS_Data %>%
  mutate(
    log_Total_AfT = log1p(USD_Disbursement),
    log_Other_AfT = log1p(Other_AfT), 
    across(c(COL_FR, COL_UK, COL_US, COL_JP), ~ ifelse(is.na(.), 0, .)),
    col_history = COL_FR + COL_UK + COL_US + COL_JP,
    proximity = -log(distwces),
    log_Foreign = log1p(Foreign_pop),
    log_VA          = log1p(VA),
    VA_share = VA / total_exports_donor,
    Cost_Trade_inv = -Cost_Trade,
  ) %>%
  arrange(DonorName, RecipientName, Year) %>%
  group_by(DonorName, RecipientName) %>%
  mutate(across(c(log_Other_AfT, total_reserves, gdp_growth, external_debt,
                  total_asym, VA, VA_share),
                ~ lag(.), .names = "{.col}_lag")) %>%
  ungroup()
```

```{r}
winsor_top <- function(x, p = 0.99) pmin(x, quantile(x, p, na.rm = TRUE))

CRS_Data <- CRS_Data %>%
  mutate(
    external_debt_lag  = winsor_top(external_debt_lag,  0.99),
    total_reserves_lag = winsor_top(total_reserves_lag, 0.99)
  )
```

```{r}
write_xlsx(CRS_Data, here::here("data/processed/CRS_Data2.xlsx"))
```

### Equal weighting (formative) construct building:

```{r}
# EBT — Bargaining power (alpha) construction
# Formative, equal-weighted composite of four dimensions.
#
# Outside options are NOT folded into alpha: in the SUR,
#   log_Other_AfT_lag      enters as the recipient threat point d_R (+)
#   donor_threat_dyad_lag  enters as the donor threat point   d_D (-)
# alpha is the relative-power weight; the threat points are separate.
#
# Two urgency specs are built:
#   alpha_core  = urgency from reserves / growth / debt only  (PRIMARY)
#   alpha_ext   = urgency also including eci + Cost_Trade      (ROBUSTNESS)

## z-score that ignores NAs and leaves NA positions as NA
z <- function(x) (x - mean(x, na.rm = TRUE)) / sd(x, na.rm = TRUE)
```

```{r}
## Extra indicators for the urgency robustness:
CRS_Data <- CRS_Data %>%
  arrange(DonorName, RecipientName, Year_int) %>%
  group_by(DonorName, RecipientName) %>%
  mutate(
    eci_lag            = lag(eci),
    Cost_Trade_inv_lag = lag(Cost_Trade_inv)
  ) %>%
  ungroup()
```

```{r}
## Oriented z-scores (all signed so higher = higher recipient power):
CRS_Data <- CRS_Data %>%
  mutate(
    # urgency / crisis
    z_reserves = z(total_reserves_lag),        # +
    z_growth   = z(gdp_growth_lag),            # +
    z_debt     = -z(external_debt_lag),        # -  (debt = distress)
    z_eci      = z(eci_lag),                   # +  (variant only)
    z_cost     = z(Cost_Trade_inv_lag),        # +  (variant only; already inverted)
    # geopolitical stake (donor interest -> worse donor outside option)
    z_foreign  = z(log_Foreign),               # +
    z_agree    = z(agree),                     # +
    z_prox     = z(proximity),                 # +
    z_col      = z(col_history),               # +
    # commercial asymmetric dependence
    z_asym     = z(total_asym_lag),            # +
    z_vashare  = z(VA_share_lag),              # +
    # institutional capacity (reflective WGI block)
    z_cc = z(cc), z_ge = z(ge), z_pv = z(pv), z_rq = z(rq)   # +
  )
```

```{r}
## Dimension scores: mean of oriented z-scores (use what's present)
##  na.rm = TRUE so a dimension survives partial missingness; this matters
##  most for commercial (total_asym + VA_share both have gaps).
CRS_Data <- CRS_Data %>%
  mutate(
    dim_urgency_core = rowMeans(cbind(z_reserves, z_growth, z_debt), na.rm = TRUE),
    dim_urgency_ext  = rowMeans(cbind(z_reserves, z_growth, z_debt, z_eci, z_cost), na.rm = TRUE),
    dim_geo          = rowMeans(cbind(z_foreign, z_agree, z_prox, z_col), na.rm = TRUE),
    dim_comm         = rowMeans(cbind(z_asym, z_vashare), na.rm = TRUE),
    dim_inst         = rowMeans(cbind(z_cc, z_ge, z_pv, z_rq), na.rm = TRUE)
  ) %>%
  mutate(across(starts_with("dim_"), ~ ifelse(is.nan(.), NA, .)))   # all-NA row -> NA
```

```{r}
## Re-standardise each dimension before averaging into alpha
##  Averaging z-scores shrinks variance unevenly across dimensions, so a raw
##  cross-dimension mean would weight the higher-variance dimensions more.
##  Re-standardising each dimension to SD 1 is what makes the final average a
##  genuine EQUAL weighting of the four dimensions.
CRS_Data <- CRS_Data %>%
  mutate(
    s_urgency_core = z(dim_urgency_core),
    s_urgency_ext  = z(dim_urgency_ext),
    s_geo          = z(dim_geo),
    s_comm         = z(dim_comm),
    s_inst         = z(dim_inst)
  )
```

```{r}
## alpha = equal-weight mean of the four standardised dimensions:
CRS_Data <- CRS_Data %>%
  mutate(
    n_dims_core = rowSums(!is.na(cbind(s_urgency_core, s_geo, s_comm, s_inst))),
    n_dims_ext  = rowSums(!is.na(cbind(s_urgency_ext,  s_geo, s_comm, s_inst))),
    alpha_core  = rowMeans(cbind(s_urgency_core, s_geo, s_comm, s_inst), na.rm = TRUE),
    alpha_ext   = rowMeans(cbind(s_urgency_ext,  s_geo, s_comm, s_inst), na.rm = TRUE)
  ) %>%
  mutate(across(c(alpha_core, alpha_ext), ~ ifelse(is.nan(.), NA, .)))
```

```{r}
## Diagnostics:
cat("\n--- Dimension coverage per row (core alpha) ---\n")
print(table(CRS_Data$n_dims_core))
cat("Share of rows with all four dimensions:",
    round(mean(CRS_Data$n_dims_core == 4, na.rm = TRUE), 3), "\n")

cat("\n--- Dimension inter-correlations (modest = healthy formative) ---\n")
print(round(cor(CRS_Data[, c("s_urgency_core","s_geo","s_comm","s_inst")],
                use = "pairwise.complete.obs"), 2))

cat("\n--- alpha_core summary ---\n")
print(summary(CRS_Data$alpha_core))

cat("\n--- alpha vs outcomes (CIRCULARITY CHECK — want modest |r|) ---\n")
print(round(cor(cbind(alpha   = CRS_Data$alpha_core,
                      flow    = log1p(CRS_Data$USD_Disbursement),
                      channel = CRS_Data$ChannelBalance,
                      trade   = CRS_Data$preference_margin),
                use = "pairwise.complete.obs"), 2))

cat("\n--- core vs extended alpha (should be very highly correlated) ---\n")
print(round(cor(CRS_Data$alpha_core, CRS_Data$alpha_ext,
                use = "pairwise.complete.obs"), 3))
```

```{r}
summary(CRS_Data$USD_Disbursement)
sum(CRS_Data$USD_Disbursement < 0, na.rm = TRUE)
```

```{r}
# Floor AfT flows at 0 to get rid of 7 negative flows:
CRS_Data$flow_log <- log1p(pmax(CRS_Data$USD_Disbursement, 0))
```

```{r}
write_xlsx(CRS_Data, here::here("data/processed/CRS_Data3.xlsx"))
```

### SUR specification:

```{r}
# ============================================================
# EBT — Between-dyad SUR of the three negotiation outcomes
#
# Three jointly-estimated equations:
#   flow     = flow_log         (aid size)
#   channel  = ChannelBalance   (design command)
#   trade    = preference_margin (policy concession; = mfn_rate - eff_tariff)
#
# Regressors (the Nash structure):
#   alpha_z  relative bargaining power           (the four-dimension composite)
#   dR_z     recipient threat point  log_Other_AfT_lag      (+)
#   dD_z     donor threat point      donor_threat_dyad_lag  (-)
#   Year_f   year fixed effects
#
# NO dyad FE: alpha is ~entirely between-dyad, so dyad FE collapse the system.
# Identification is off cross-dyad variation, which is the theoretically
# relevant variation (bargaining power is a structural feature of a dyad).
# ============================================================

# Estimation frame: four-complete alpha + all model vars present
est <- CRS_Data %>%
  filter(n_dims_core == 4,
         !is.na(alpha_core), !is.na(flow_log), !is.na(ChannelBalance),
         !is.na(preference_margin),
         !is.na(log_Other_AfT_lag), !is.na(donor_threat_dyad_lag)) %>%
  mutate(Year_f  = droplevels(factor(Year_int)),
         alpha_z = z(alpha_core),
         dR_z    = z(log_Other_AfT_lag),
         dD_z    = z(donor_threat_dyad_lag))

cat("Estimation N:", nrow(est),
    "| dyads:", dplyr::n_distinct(paste(est$DonorName, est$RecipientName)), "\n")

# Collinearity check first:
cat("\n--- Correlations among the three power regressors ---\n")
print(round(cor(est[, c("alpha_z", "dR_z", "dD_z")]), 2))

cat("\n--- VIFs (read the alpha_z / dR_z / dD_z rows; want well under 5) ---\n")
print(vif(lm(flow_log ~ alpha_z + dR_z + dD_z + Year_f, data = est)))
```

```{r}
# Descriptives:

## Structural vs dynamic variance of alpha:
bw <- est %>% group_by(DonorName, RecipientName) %>%
  mutate(a_between = mean(alpha_core), a_within = alpha_core - a_between) %>% ungroup()
vb <- var(bw$a_between); vw <- var(bw$a_within)
cat("between share:", round(vb/(vb+vw), 3), "| within share:", round(vw/(vb+vw), 3), "\n")

## Donor-level distribution of recipient power:
donor_tab <- est %>%
  group_by(DonorName, RecipientName) %>% summarise(m = mean(alpha_core), .groups="drop") %>%
  group_by(DonorName) %>%
  summarise(mean_alpha = round(mean(m),3), pct_below_0 = round(mean(m<0)*100,1),
            n_dyads = n(), .groups="drop") %>% arrange(mean_alpha)
print(donor_tab)

## Figure 4:
fig4 <- est %>% group_by(DonorName, RecipientName) %>% summarise(m = mean(alpha_core), .groups="drop")
ggplot(fig4, aes(DonorName, m)) +
  geom_violin(alpha = .5, colour = "grey", fill = "grey") + geom_boxplot(width = .15, outlier.size = .5) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = NULL, y = "Mean recipient bargaining power (alpha)") +
  theme_minimal(base_size = 12) + theme(legend.position = "none")
```

```{r}
# Collinearity check + SUR + residual correlations:
print(round(cor(est[, c("alpha_z","dR_z","dD_z")]), 2))
print(vif(lm(flow_log ~ alpha_z + dR_z + dD_z + Year_f, data = est)))

sur <- systemfit(list(
  flow    = flow_log          ~ alpha_z + dR_z + dD_z + Year_f,
  channel = ChannelBalance    ~ alpha_z + dR_z + dD_z + Year_f,
  trade   = preference_margin ~ alpha_z + dR_z + dD_z + Year_f),
  method = "SUR", data = est)
print(summary(sur))
print(round(cor(residuals(sur)), 3))    # Table 2 / prediction P2(a): residual correlation matrix
```

#### Dyad cluster-bootstrap of the WHOLE pipeline  (the central inference fix):

```{r}
# Bargaining power is an estimated regressor, so honest SEs require re-estimating the PLS construct inside each resample. Cluster on dyad; keep boot_mat for the marginal-effect CIs in step 6b.
```

```{r}
# EBT — Dyad cluster bootstrap:

## build_alpha and fit_coefs now use the same dimension names as the construction (s_urgency_core, n_dims_core), z is gone from here (it's global), and fit_coefs is extended to capture the flow and channel decompositions too, so the whole of Table 4 comes out of one run with intervals:

build_alpha <- function(df) {
  df %>%
    mutate(
      z_reserves = z(total_reserves_lag), z_growth = z(gdp_growth_lag), z_debt = -z(external_debt_lag),
      z_foreign = z(log_Foreign), z_agree = z(agree), z_prox = z(proximity), z_col = z(col_history),
      z_asym = z(total_asym_lag), z_vashare = z(VA_share_lag),
      z_cc = z(cc), z_ge = z(ge), z_pv = z(pv), z_rq = z(rq)
    ) %>%
    mutate(
      dim_urgency_core = rowMeans(cbind(z_reserves, z_growth, z_debt), na.rm = TRUE),
      dim_geo  = rowMeans(cbind(z_foreign, z_agree, z_prox, z_col), na.rm = TRUE),
      dim_comm = rowMeans(cbind(z_asym, z_vashare), na.rm = TRUE),
      dim_inst = rowMeans(cbind(z_cc, z_ge, z_pv, z_rq), na.rm = TRUE)
    ) %>%
    mutate(across(starts_with("dim_"), ~ ifelse(is.nan(.), NA, .))) %>%
    mutate(
      s_urgency_core = z(dim_urgency_core), s_geo = z(dim_geo), s_comm = z(dim_comm), s_inst = z(dim_inst),
      n_dims_core = rowSums(!is.na(cbind(s_urgency_core, s_geo, s_comm, s_inst))),
      alpha_core  = rowMeans(cbind(s_urgency_core, s_geo, s_comm, s_inst), na.rm = TRUE),
      alpha_core  = ifelse(is.nan(alpha_core), NA, alpha_core)
    )
}

fit_coefs <- function(df) {
  d <- df %>%
    filter(n_dims_core == 4,
           !is.na(alpha_core), !is.na(flow_log), !is.na(ChannelBalance),
           !is.na(preference_margin), !is.na(log_Other_AfT_lag), !is.na(donor_threat_dyad_lag)) %>%
    mutate(Year_f = factor(Year_int), alpha_z = z(alpha_core),
           dR_z = z(log_Other_AfT_lag), dD_z = z(donor_threat_dyad_lag))
  g <- function(m, t) unname(coef(m)[t]); D <- c("s_urgency_core","s_geo","s_comm","s_inst")

  mf <- lm(flow_log ~ alpha_z + dR_z + dD_z + Year_f, d)
  mc <- lm(ChannelBalance ~ alpha_z + dR_z + dD_z + Year_f, d)
  mt <- lm(preference_margin ~ alpha_z + dR_z + dD_z + Year_f, d)

  # Decomposition is jointly estimated as a SUR (same regressors in all three
  # equations, so coefficients match per-equation OLS exactly; kept as SUR here
  # so the resampled object matches the aggregate model's estimator):
  sur_dec <- systemfit(list(
    flow    = flow_log          ~ s_urgency_core + s_geo + s_comm + s_inst + dR_z + dD_z + Year_f,
    channel = ChannelBalance    ~ s_urgency_core + s_geo + s_comm + s_inst + dR_z + dD_z + Year_f,
    trade   = preference_margin ~ s_urgency_core + s_geo + s_comm + s_inst + dR_z + dD_z + Year_f),
    method = "SUR", data = d)
  gs <- function(eq, t) unname(coef(sur_dec)[paste0(eq, "_", t)])

  c(flow_alpha=g(mf,"alpha_z"),  flow_dR=g(mf,"dR_z"),  flow_dD=g(mf,"dD_z"),
    chan_alpha=g(mc,"alpha_z"),  chan_dR=g(mc,"dR_z"),  chan_dD=g(mc,"dD_z"),
    trade_alpha=g(mt,"alpha_z"), trade_dR=g(mt,"dR_z"), trade_dD=g(mt,"dD_z"),
    flow_urg=gs("flow",D[1]),    flow_geo=gs("flow",D[2]),    flow_comm=gs("flow",D[3]),    flow_inst=gs("flow",D[4]),
    chan_urg=gs("channel",D[1]), chan_geo=gs("channel",D[2]), chan_comm=gs("channel",D[3]), chan_inst=gs("channel",D[4]),
    trade_urg=gs("trade",D[1]),  trade_geo=gs("trade",D[2]),  trade_comm=gs("trade",D[3]),  trade_inst=gs("trade",D[4]))
}

point <- fit_coefs(build_alpha(CRS_Data))

set.seed(123); B <- 2000
CRS_Data$dyad_id <- paste(CRS_Data$DonorName, CRS_Data$RecipientName)
dyads <- unique(CRS_Data$dyad_id); dyad_rows <- split(seq_len(nrow(CRS_Data)), CRS_Data$dyad_id)
K <- length(point)
boot <- matrix(NA_real_, B, K, dimnames = list(NULL, names(point)))
for (b in seq_len(B)) {
  idx <- unlist(dyad_rows[sample(dyads, length(dyads), replace = TRUE)], use.names = FALSE)
  boot[b, ] <- tryCatch(fit_coefs(build_alpha(CRS_Data[idx, ])), error = function(e) rep(NA_real_, K))
  if (b %% 100 == 0) cat("resample", b, "of", B, "\n")
}

res <- data.frame(coef = names(point), estimate = round(point,4),
  boot_se = round(apply(boot,2,sd,na.rm=TRUE),4),
  ci_lo = round(apply(boot,2,quantile,.025,na.rm=TRUE),4),
  ci_hi = round(apply(boot,2,quantile,.975,na.rm=TRUE),4))
res$sig <- ifelse(res$ci_lo > 0 | res$ci_hi < 0, "*", "")
print(res, row.names = FALSE)
```

```{r}
vif(lm(preference_margin ~ s_urgency_core + s_geo + s_comm + s_inst + dR_z + dD_z + Year_f, data = est))
```
#### P1 — power shapes all three outcomes simultaneously:

```{r}
# The per-equation intervals in res are the primary P1 evidence, but this is the system-level "alpha is jointly non-zero" summary of
```

```{r}
bp_terms <- c("flow_alpha", "chan_alpha", "trade_alpha")
V <- cov(boot[, bp_terms], use = "complete.obs")
W <- as.numeric(t(point[bp_terms]) %*% solve(V) %*% point[bp_terms])
cat("Joint Wald W =", round(W,2), " p =", signif(pchisq(W, length(bp_terms), lower.tail = FALSE), 3), "\n")
```

#### P2 — trade-offs, two pieces, no interaction terms:

```{r}
# P2 — two pieces, both already produced above.

## Piece (a) is the residual-correlation matrix from the SUR estimation above (cor(residuals(sur))); the live cell is the positive flow–channel correlation, read as co-movement/complementarity, with a negative off-diagonal being the conditional trade-off.

## Piece (b) is the decomposition rows of res (*_urg/geo/comm/inst), where commercial sitting below zero against geopolitical/institutional above it is the heterogeneity result. There is no quadratic marginal-effects step any more.
```

#### Breusch-Pagan test:

```{r}
R <- cor(residuals(sur)); Tn <- nrow(est)
LM <- Tn * sum(R[lower.tri(R)]^2)
cat("Breusch-Pagan LM =", round(LM, 1), "| df =", choose(ncol(R), 2),
    "| p =", signif(pchisq(LM, choose(ncol(R), 2), lower.tail = FALSE), 3), "\n")
```

#### Trade-off test:

```{r}
# terciles by dyad-mean power, so each dyad sits wholly in one group
est <- est %>%
  group_by(DonorName, RecipientName) %>% mutate(alpha_dyad = mean(alpha_z)) %>% ungroup() %>%
  mutate(alpha_grp = ntile(alpha_dyad, 3))          # 1 = lowest power, 3 = highest

# the three residual correlations for a given data frame
rcor <- function(d) {
  rf <- residuals(lm(flow_log          ~ alpha_z + dR_z + dD_z + Year_f, d))
  rc <- residuals(lm(ChannelBalance    ~ alpha_z + dR_z + dD_z + Year_f, d))
  rt <- residuals(lm(preference_margin ~ alpha_z + dR_z + dD_z + Year_f, d))
  R  <- cor(cbind(rf, rc, rt)); c(fc = R[1,2], ft = R[1,3], ct = R[2,3])
}

pooled_point <- rcor(est)
grp_point    <- sapply(1:3, function(g) rcor(droplevels(filter(est, alpha_grp == g))))

set.seed(123); B <- 2000
est$dyad_id <- paste(est$DonorName, est$RecipientName)
dyads <- unique(est$dyad_id); drows <- split(seq_len(nrow(est)), est$dyad_id)

bp <- matrix(NA_real_, B, 3, dimnames = list(NULL, names(pooled_point)))
bg <- array(NA_real_, c(B, 3, 3))
for (b in 1:B) {
  idx <- unlist(drows[sample(dyads, length(dyads), TRUE)], use.names = FALSE)
  db  <- est[idx, ]
  bp[b, ] <- tryCatch(rcor(db), error = function(e) rep(NA_real_, 3))
  for (g in 1:3) {
    sub <- droplevels(db[db$alpha_grp == g, ])
    bg[b, , g] <- tryCatch(rcor(sub), error = function(e) rep(NA_real_, 3))
  }
  if (b %% 200 == 0) cat("resample", b, "\n")
}

ci <- function(x) quantile(x, c(.025, .975), na.rm = TRUE)
nm <- c("flow-channel","flow-trade","channel-trade")

cat("\n=== Pooled residual correlations (95% CI) ===\n")
for (k in 1:3) cat(sprintf("  %-14s % .3f [% .3f, % .3f]%s\n", nm[k], pooled_point[k],
  ci(bp[,k])[1], ci(bp[,k])[2], ifelse(ci(bp[,k])[1] > 0 | ci(bp[,k])[2] < 0, " *", "")))

cat("\n=== By alpha tercile, with high-low difference ===\n")
for (k in 1:3) {
  cat(nm[k], ":\n", sep = "")
  for (g in 1:3) cat(sprintf("  %-4s % .3f [% .3f, % .3f]\n", c("low","mid","high")[g],
    grp_point[k,g], ci(bg[,k,g])[1], ci(bg[,k,g])[2]))
  d <- bg[,k,3] - bg[,k,1]
  cat(sprintf("  high-low % .3f [% .3f, % .3f]%s\n", grp_point[k,3]-grp_point[k,1],
    ci(d)[1], ci(d)[2], ifelse(ci(d)[1] > 0 | ci(d)[2] < 0, " *", "")))
}
```

### Discussion figures:

```{r}
# Figure 4 — cross-equation residual correlations by bargaining-power tercile:

pairs_nm <- c("Flow – Channel", "Flow – Policy", "Channel – Policy")  # bg/grp_point order: fc, ft, ct
terc_nm  <- c("Low", "Mid", "High")

fig_df <- do.call(rbind, lapply(1:3, function(p) do.call(rbind, lapply(1:3, function(g) {
  data.frame(pair = pairs_nm[p], terc = terc_nm[g],
             est = grp_point[p, g],
             lo  = quantile(bg[, p, g], 0.025, na.rm = TRUE),
             hi  = quantile(bg[, p, g], 0.975, na.rm = TRUE))
}))))
fig_df$pair <- factor(fig_df$pair, levels = pairs_nm)
fig_df$terc <- factor(fig_df$terc, levels = terc_nm)

ggplot(fig_df, aes(terc, est, group = pair, colour = pair)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey55") +
  geom_line(position = position_dodge(0.35), linewidth = 0.7) +
  geom_pointrange(aes(ymin = lo, ymax = hi),
                  position = position_dodge(0.35), size = 0.7) +
  scale_colour_manual(values = c("Flow – Channel"   = "#6E9FC6",
                                 "Flow – Policy"     = "#d6604d",
                                 "Channel – Policy"  = "#ACD4EC")) +
  labs(x = "Recipient bargaining-power tercile",
       y = "Cross-equation residual correlation (95% CI)", colour = NULL) +
  theme_minimal(base_size = 12) +
  theme(axis.title.y = element_text(size = 11),
        axis.title.x = element_text(size = 11),
        legend.position = "right", panel.grid.minor = element_blank())
 ggsave(here::here("output/figures/Figure4_complementarity_gradient.png"), width = 7, height = 4.2, dpi = 300)
```

### Robustness:

```{r}
# Both robustness checks below use donor + recipient (NOT full dyad) fixed
# effects instead of the main dyad-level SUR: alpha is overwhelmingly
# between-dyad (see Descriptives above), so dyad FE would absorb it, but
# donor and recipient FE separately still leave alpha's between-dyad
# variation identified, while soaking up time-invariant donor- and
# recipient-level confounds. Checked in the order they appear in the paper.
```

#### Appendix B — Alternative trade DV, under donor + recipient fixed effects:

```{r}
# Primary DV is preference_margin (mfn_rate - eff_tariff); the alternative is
# trade_concession (-eff_tariff, raw levels, not MFN-netted). Same est sample
# as the main SUR (n_dims_core == 4 + all model vars present).

est$dyad_id <- paste(est$DonorName, est$RecipientName)

feB_primary <- fixest::feols(preference_margin ~ alpha_z + dR_z + dD_z | DonorName + RecipientName + Year_f,
                              cluster = ~dyad_id, data = est)
feB_alt     <- fixest::feols(trade_concession  ~ alpha_z + dR_z + dD_z | DonorName + RecipientName + Year_f,
                              cluster = ~dyad_id, data = est)

etable(feB_primary, feB_alt,
       headers = c("preference_margin (primary)", "trade_concession (alt.)"))
```

#### Appendix C — Augmented bargaining-power composite, under donor + recipient fixed effects:

```{r}
# alpha_core (primary) vs alpha_ext (augments the resilience dimension with
# eci and inverted cost-of-trade). Sample is held fixed across both
# composites (n_dims_core == 4 AND n_dims_ext == 4) so the comparison
# isolates the composite-construction choice, not sample composition.

est_ext <- CRS_Data %>%
  filter(n_dims_core == 4, n_dims_ext == 4,
         !is.na(alpha_core), !is.na(alpha_ext),
         !is.na(flow_log), !is.na(ChannelBalance), !is.na(preference_margin),
         !is.na(log_Other_AfT_lag), !is.na(donor_threat_dyad_lag)) %>%
  mutate(Year_f      = droplevels(factor(Year_int)),
         alpha_z     = z(alpha_core),
         alpha_ext_z = z(alpha_ext),
         dR_z        = z(log_Other_AfT_lag),
         dD_z        = z(donor_threat_dyad_lag),
         dyad_id     = paste(DonorName, RecipientName))

cat("Appendix C estimation N:", nrow(est_ext),
    "| dyads:", dplyr::n_distinct(est_ext$dyad_id),
    "| corr(alpha_core, alpha_ext) on this sample:",
    round(cor(est_ext$alpha_core, est_ext$alpha_ext), 3), "\n")

flow_core  <- fixest::feols(flow_log          ~ alpha_z     + dR_z + dD_z | DonorName + RecipientName + Year_f, cluster = ~dyad_id, data = est_ext)
flow_ext   <- fixest::feols(flow_log          ~ alpha_ext_z + dR_z + dD_z | DonorName + RecipientName + Year_f, cluster = ~dyad_id, data = est_ext)
chan_core  <- fixest::feols(ChannelBalance    ~ alpha_z     + dR_z + dD_z | DonorName + RecipientName + Year_f, cluster = ~dyad_id, data = est_ext)
chan_ext   <- fixest::feols(ChannelBalance    ~ alpha_ext_z + dR_z + dD_z | DonorName + RecipientName + Year_f, cluster = ~dyad_id, data = est_ext)
trade_core <- fixest::feols(preference_margin ~ alpha_z     + dR_z + dD_z | DonorName + RecipientName + Year_f, cluster = ~dyad_id, data = est_ext)
trade_ext  <- fixest::feols(preference_margin ~ alpha_ext_z + dR_z + dD_z | DonorName + RecipientName + Year_f, cluster = ~dyad_id, data = est_ext)

etable(flow_core, flow_ext, chan_core, chan_ext, trade_core, trade_ext,
       headers = c("flow (core)", "flow (ext)", "channel (core)", "channel (ext)", "trade (core)", "trade (ext)"))
```
